Topological Equivariant Artist Model

### 2022-01-12 slides/main.tex
flip pullback arrow

%add transition slide

%move other side to when I introduce Q 
\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}

    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha", Rightarrow, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor] \arrow[rr, "G"', bend right, color=functor] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
    \end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:2->{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:2->{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:4-5>{\arrow[rr, "\alpha_{c}", bend left, color=nattran]}  
            \onslide*<6|handout:6>{\arrow[rr, "\alpha_{c}", color=nattran]} \& 
            \onslide*<1-4|handout:1-4>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1-4>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:3-4>{\arrow[r, "G"', color=functor]}
            \onslide*<2-4|handout:2-4>{\arrow[l, "F", color=functor]} \& 
            \onslide*<3-|handout:3->{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:3->{\arrow[dd, "G(f)", color=target]} \\
            {} 
            \onslide*<4|handout:4>{\arrow[rr, dotted, color=nattran]}
            \onslide*<5|handout:5>{\arrow[rr, color=nattran]} \& \& {}                      \\
            \onslide*<2-|handout:2->{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:4-5>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran]} 
            \onslide*<4-5|handout:6>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran]}\& 
            \onslide*<1-4|handout:1-4>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:2-4>{\arrow[l, "F"', color=functor]} 
            \onslide*<3-4|handout:3-4>{\arrow[r, "G", color=functor]} \& 
            \onslide*<3-|handout:3->{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}    
\end{frame}

\begin{frame}{$\vartist_{\vindexpushc}: \sheafc_{(\dbasec, \dtotalc)} \rightarrow \vindexpushc\sheafc_{(\gbasec, \gtotalc)}$}
    \begin{equation}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dtotalc}", color=sheaf] 
        \arrow[rr, "\sheafc_{\gtotalpushc}"', color=sheaf] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist] &&&& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dtotalc}"', color=sheaf] 
        \arrow[rr, "\sheafc_{\gtotalpushc}", color=sheaf] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
    \end{equation}
\end{frame}

\begin{frame}{$\vartist_{\vindexpullc}: \vindexpullc\sheafc_{(\dbasec, \dtotalc)} \rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \begin{equation}
  \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist] &&&& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}                                                        
\end{tikzcd}
\end{equation}
\end{frame}

\begin{frame}{
    \only<1-3|handout:1-3>{Natural Transforms Between Sheaves}
    \only<4|handout:4>{$\vartistc:\sheafc_{(\dbasec, \dtotalc)}\rightarrow \sheafc_{(\gbasec, \gtotalc)}$}
    \only<5-|handout:5->{$\vartistc: \dsectionc \mapsto \gsectionc$}
    }
    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<1-4|handout:1>{\sheafc_{\gbasec, \gtotalc}\gbasec} 
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpushc", color=artist]} 
          \& \& 
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})(\dbase)}
          \\
          \& \& \\
          \onslide*<1-4|handout:1>{(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)})(\gbasec)}
          \onslide*<1-3|handout:1>{\arrow[rr, "\textcolor{functor}{\vindexpull}", color=functor]}
          \onslide*<4-|handout:2->{\arrow[rr, "\vindexpullc", color=artist]}
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\gbasec}}", color=nattran]} 
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist]}
          \&  \& 
          \onslide*<1-4|handout:1->{\sheafc_{\dbasec, \dtotalc}} 
          \onslide*<2-3|handout:1>{\arrow[uu, "\textcolor{nattran}{Nat_{\dbasec}}"', color=nattran]}
          \onslide*<4-|handout:2->{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist]}
          \onslide*<3|handout:1>{\arrow[lluu, " "' description, dashed, color=nattran]}
          \onslide*<4-|handout:2->{\arrow[lluu, "\vartistc"' description, dashed, color=artist]}
        \end{tikzcd}
      \end{equation*}

    \onslide<3|handout:3>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\gbasec}(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)}, \sheafc_{(\gbasec, \gtotalc)}) = 
    \textcolor{nattran}{Nat}_{\dbase}(\sheafc_{(\dbasec, \dtotalc)}, \textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})
        \end{equation*}
    }
    \onslide<4|handout:4>{
        \begin{equation*}
            \vartistc_{\vindexpull} = \vartistc_{\vindexpush}
        \end{equation*}
    }
\end{frame}

>>>>

%add transition slide->possibly call back 
\begin{frame}
    {\huge
        \begin{equation*}
            \sheafc_{\dbasec,\dtotalc} \textcolor{artist}{\xrightarrow{\vartistc}} \sheafc_{\gbasec, \gtotalc}
        \end{equation*}
    }
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\mapsto} \textcolor{functor}{G}$}

    \adjustbox{scale=3, center}{
        \begin{tikzcd}[ampersand replacement=\&]
            \& {} \arrow[dd, "\alpha" , maps to, shorten=1.5em, color=nattran] \&             \\
          \textcolor{source}{\mathcal{C}} \arrow[rr, "F", bend left, color=functor, maps to] \arrow[rr, "G"', bend right, color=functor, maps to] \& \& \textcolor{target}{\mathcal{D}} \\
            \& {} \&            
          \end{tikzcd}}
\end{frame}

\begin{frame}{Natural Transformation $\textcolor{nattran}{\alpha}: \textcolor{functor}{F} \textcolor{nattran}{\rightarrow} \textcolor{functor}{G}$}
    \begin{equation*}
        \begin{tikzcd}[column sep=huge, ampersand replacement = \&]
            \onslide*<2-|handout:1>{\textcolor{target}{F(c)}}
            \onslide*<2-|handout:1>{\arrow[dd, "F(f)"', color=target]}
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c}", bend left, color=nattran, maps to]}  
            \onslide*<6|handout:0>{\arrow[rr, "\alpha_{c}", color=nattran, maps to]} \& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c}} 
            \onslide*<1-4|handout:1>{\arrow[dd, "f" description, color=source]}
            \onslide*<3-4|handout:1>{\arrow[r, "G"', color=functor,maps to ]}
            \onslide*<2-4|handout:1>{\arrow[l, "F", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c)}} 
            \onslide*<3-|handout:1>{\arrow[dd, "G(f)", color=target, maps to]} \\
            {} 
            \onslide*<4|handout:1>{\arrow[rr, dotted, color=nattran, maps to]}
            \onslide*<5|handout:0>{\arrow[rr, color=nattran, maps to]} \& \& {}                      \\
            \onslide*<2-|handout:1>{\textcolor{target}{F(c^{\prime})}} 
            \onslide*<4-5|handout:1>{\arrow[rr, "\alpha_{c^{\prime}}"', bend right, color=nattran, maps to]} 
            \onslide*<4-5|handout:0>{\arrow[rr, "\alpha_{c^{\prime}}"', color=nattran, maps to]}\& 
            \onslide*<1-4|handout:1>{\textcolor{source}{c^{\prime}}}
            \onslide*<2-4|handout:1>{\arrow[l, "F"', color=functor, maps to]} 
            \onslide*<3-4|handout:1>{\arrow[r, "G", color=functor, maps to]} \& 
            \onslide*<3-|handout:1>{\textcolor{target}{G(c^{\prime})}}          
        \end{tikzcd}
    \end{equation*}    
\end{frame}

\begin{frame}
    \frametitle<1-2|handout:1>{Data Space: $\vartistc_{\vindexpushc}: \sheafc_{\dbasec, \dtotalc} \textcolor{artist}{\mapsto} \vindexpushc\sheafc_{\gbasec, \gtotalc}$}
    \frametitle<3-4|handout:2>{Display Space: $\vartist_{\vindexpullc}: \vindexpullc\sheafc_{\dbasec, \dtotalc} \rightarrow \sheafc_{\gbasec, \gtotalc}$}
    \frametitle<5|handout:3->{\textcolor{artist}{Artist} \vartistc}

    \onslide*<1|handout:1>{
        \begin{equation*}
      \begin{tikzcd}[ampersand replacement =\&]
        \cgamma{\opensetc_1}{\dtotalc} 
        \arrow[dd, "\iota^*"', hook, color=set] 
        \arrow[rrrr, "\vartistc_{\opensetc_1}", bend left, color=artist, maps to] \&  \& 
        \opensetc_1 
        \arrow[ll, "\sheafc_{\dtotalc}", color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}"', color=sheaf, maps to] \&  \& 
        \cgamma{\opensetc_1}{\gtotalpushc} 
        \arrow[dd, "\iota^*", hook', color=set] \\
        {} 
        \arrow[rrrr, dotted, color=artist, maps to] \&\&\&\& {} \\
        \cgamma{\opensetc_2}{\dtotalc} 
        \arrow[rrrr, "\vartistc_{\opensetc_2}"', bend right, color=artist, maps to] \&  \& 
        \opensetc_2 
        \arrow[ll, "\sheafc_{\dtotalc}"', color=sheaf, maps to] 
        \arrow[rr, "\sheafc_{\gtotalpushc}", color=sheaf, maps to] 
        \arrow[uu, "\iota" description, hook, color=base] \& \& 
        \cgamma{\opensetc_2}{\gtotalpushc}               
    \end{tikzcd}
        \end{equation*}}

    \onslide*<0|handout:2>{
        \begin{equation*}
  \begin{tikzcd}[ampersand replacement =\&]
    \cgamma{\opensetgc_1}{\dtotalpullc} 
    \arrow[dd, "\iota^*"', hook, color=set] 
    \arrow[rrrr, "\vartistc_{\opensetgc_1}", bend left, color=artist, maps to] \&  \& 
    \opensetgc_1 
    \arrow[ll, "\sheafc_{\dtotalpullc}", color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}"', color=sheaf, maps to] \&  \& 
    \cgamma{\opensetgc_1}{\gtotalc} 
    \arrow[dd, "\iota^*", hook', color=set] \\
    {} 
    \arrow[rrrr, dotted, color=artist, maps to] \&\&\&\& {} \\
    \cgamma{\opensetgc_2}{\dtotalpullc} 
    \arrow[rrrr, "\vartistc_{\opensetgc_2}"', bend right, color=artist, maps to] \&  \& 
    \opensetgc_2 
    \arrow[ll, "\sheafc_{\dtotalpullc}"', color=sheaf, maps to] 
    \arrow[rr, "\sheafc_{\gtotalc}", color=sheaf, maps to] 
    \arrow[uu, "\iota" description, hook, color=base] \& \& 
    \cgamma{\opensetgc_2}{\gtotalc}   
\end{tikzcd}
    \end{equation*}}

    \begin{equation*}
        \begin{tikzcd}[ampersand replacement=\&]
          \onslide*<0|handout:3>{\sheafc_{\gbasec, \gtotalc}} 
          \onslide*<0|handout:3>{\arrow[rr, "\textcolor{functor}{\vindexpush}", color=functor]}  
          \& \& 
          \onslide*<0|handout:3>{\textcolor{functor}{\vindexpush}\sheafc_{\gbasec, \gtotalc}}
          \\
          \& \& \\
          \onslide*<0|handout:3>{\textcolor{functor}{\vindexpull}\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3>{\arrow[uu, "\vartistc_{\vindexpushc}", color=artist, maps to]}
          \&  \& 
          \onslide*<0|handout:3>{\sheafc_{\dbasec, \dtotalc}}
          \onslide*<0|handout:3>{\arrow[ll, "\textcolor{functor}{\vindexpull}", color=functor]} 
          \onslide*<0|handout:3>{\arrow[uu, "\vartistc_{\vindexpullc}"', color=artist, maps to]}
          \onslide*<4-|handout:3>{\arrow[lluu, "\vartistc"' description, dashed, color=artist, maps to]}
        \end{tikzcd}
      \end{equation*}

    \onslide<0|handout:3>{
        \begin{equation*}
        \textcolor{nattran}{Nat}_{\gbasec}(\textcolor{functor}{\vindexpull}\sheafc_{(\dbasec, \dtotalc)}, \sheafc_{(\gbasec, \gtotalc)}) = 
    \textcolor{nattran}{Nat}_{\dbase}(\sheafc_{(\dbasec, \dtotalc)}, \textcolor{functor}{\vindexpush}\sheafc_{(\gbasec, \gtotalc)})
        \end{equation*}
    }
\end{frame}
